\LARGE \bf Mean Estimation from One-Bit Measurements

### 2019-10-07 distributed-estimation.tex
went through proof of Theorem 5

\begin{thm} \label{thm:LAN1}
For $n \in \mathbb N$ and $A_n \subset \mathbb R$,  define
\begin{equation}
\label{eq:precision_general}
L_n(A_1,\ldots,A_n;\theta) \triangleq \frac{1}{n} \sum_{i=1}^n \frac{ \left(\frac{d}{d \theta} \Prob(X_i \in A_i) \right)^2 }{ \Prob(X_i \in A_i)\left(1- \Prob(X_i \in A_i) \right) }. 
\end{equation}
Consider the following conditions:
\begin{itemize}
\item [(i)\,\,] The pdf $f(x)$ of $X_n-\theta$ is log-concave, differentiable, and symmetric. Furthermore, there exists $\delta>0$ such that the function $\eta^{1+\delta}(x)/f^\delta(x)$ is non-increasing in $|x|$ and is uniquely maximized by the $x=0$. 
\item[(ii)\,] $A_n$ is a finite union of disjoint intervals.
\item[(iii)] The limit 
\begin{equation}
\label{eq:LAN_lim}
\kappa(\theta) \triangleq \lim_{n\to \infty} L_n(A_1,\ldots,A_n; \theta)
\end{equation}
exists. 
\end{itemize}
For $i=1,\ldots,n$ set
\[
B_n = \begin{cases} 1 & X_n \in A_n, \\
-1 & X_n \notin A_n. 
\end{cases} 
\]
For any $\theta$, $f(x)$ and a sequence of sets $A_1,A_2,\ldots$ such that (i)-(iii) hold, and any $h\in \mathbb R$, we have
\begin{align*}
& \log  \frac{ \mathbb P_{\theta+h/\sqrt{n}} (B_1,\ldots,B_n) }{
\mathbb P_{\theta} (B_1,\ldots,B_n)} \\
& \overset{d}{\longrightarrow} \Ncal\left(-\frac{1}{2} h^2 \kappa(\theta), h^2 \kappa(\theta) \right).
\end{align*} 
\end{thm}
Theorem~\ref{thm:LAN1} provides conditions under which $B_1,\ldots,B_n$ defines a LAN family with a precision parameter given by the limit in \eqref{eq:LAN_lim}. Condition (i) is satisfied, for example, by the normal distribution with $\delta\leq 2$. Condition (iii) is arguably the strongest and hardest to verify. As we show in Section~\ref{subsec:threshold} below, this condition is satisfied, for example, when $A_1, \ldots,A_n$ are half lines whose starting points are drawn independently from some probability measure on $\mathbb R$. Similar ideas imply that condition (iii) holds whenever we choose the intervals consisting each $A_i$ according to some pre-specified distribution. \par
%
An important conclusion of Theorem~\ref{thm:LAN1} follows from the local asymptotic minimax property of estimators in LAN models \cite{van2000asymptotic}):
\begin{cor} \label{cor:LA_minimax}
Let ${\theta}_n$ be an estimator of $\theta \in \Theta$ from $B_1,\ldots,B_n$ with detection regions $A_1,\ldots,A_n$ such that conditions (i)-(iii) of Theorem~\ref{thm:LAN1} hold. Then for any symmetric and quasi-convex function $L$, 
\begin{align*}
& \liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  \mathbb E \left[ L\left( \sqrt{n}({\theta}_{n} - \tau) \right) \right]
\\
& \qquad \qquad \qquad \qquad \geq \mathbb E \left[ L (Z/\sqrt{\kappa(\theta)}) \right],
\end{align*}
where $Z \sim \Ncal(0,1)$. In particular, for $L(x) = x^2$,
\begin{align*}
\liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  n \mathbb E  \left( {\theta}_{n} - \tau \right)^2 \geq 1/\kappa(\theta).
\end{align*}
\end{cor}
%
Corollary~\ref{cor:LA_minimax} says that when the sequence of one-bit messages defines a LAN model with respect to $\theta$, no estimator can attain MSE smaller than $1/\kappa(\theta)n + O(1/n)$ where $\kappa(\theta)$ is the precision parameter of the model. Consequently, the ARE  in such case is at most $\kappa(\theta)\sigma^2$. Furthermore, as we show next, no estimator in this setting can attain the optimal ARE of $\eta(0)\sigma^2$ uniformly over $ \Theta$.

@@

\subsection{Minimax Threshold Density}
The distribution $\lambda(dt)$ that maximizes $\kappa(\theta)$, and thus minimizes $1/\kappa(\theta)$, over the worst choice of $\theta$ in $\Theta = [-T,T]$ is given as the solution to the following optimization problem:
\begin{align}
\label{eq:var_cvx_minimax}
\begin{split}
\mathrm{maximize} \quad &  \inf_{\theta \in [-T,T]} \int \eta(t-\theta) \lambda(dt)
\\ 
\mathrm{subject~to} 
\quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) \leq 1. 
\end{split}
\end{align}
The objective function in \eqref{eq:var_cvx_minimax} is concave in $\lambda(dt)$ and hence this problem can be solved using a convex program. We denote by $\kappa^\star(T)$ the maximal value of \eqref{eq:var_cvx_minimax} and by $\lambda^\star(dt)$ the density that achieves this maximum.  
%
%By discretizing the interval $[-b,b]$ using $N_\theta$ values $\theta_1,\ldots,\theta_{N_\theta}$ and the real line using $N_\lambda$ values $\lambda_1,\ldots,\lambda_{N_\lambda}$, the discrete version of \eqref{eq:var_cvx_minimax} is the following linear program (LP) in the variables $K \in \mathbb R$ and $\lambda \in \mathbb R^{N_\lambda}$:
%\begin{align}
%\label{eq:cvx_minimax}
%\begin{split}
%\mathrm{maximize} \quad &  K \\ 
%\mathrm{subject~to} 
%\quad &  K \leq \mathbf H\lambda \\
%& \lambda \geq 0,\quad   \mathbf 1^T\lambda  \leq 1,
%\end{split}
%\end{align}
%where $\mathbf H_{i,j} = \eta(t_i - \theta_j)$, $i=1,\ldots,N_\lambda$, $j = 1,\ldots,N_\theta$. 
%\begin{rem}
%The number of variables in \eqref{eq:cvx_minimax} is $N_\lambda+1$ and number of constraints is $1 + N_\lambda + N_\theta$. Since an LP has an optimal solution at which the number of constraints for which equality holds is no smaller than the number of variables \cite{papadimitriou1998combinatorial}, there exists an optimal $\lambda$ with support over no more than $N_{\theta}$ points. Therefore, in approximating the solution of \eqref{eq:var_cvx_minimax} using 
%\eqref{eq:cvx_minimax}, it is enough to take $N_\lambda = N_\theta$.
%\end{rem}

Figure~\ref{fig:minimax_support} illustrates an approximating to $\lambda^\star(dt)$ obtained by solving a discretized version of \eqref{eq:var_cvx_minimax} for the case when $f(x)$ is the normal density with variance $\sigma^2$. The minimal asymptotic risk $\kappa^\star(\theta)$ obtained this way is illustrated in Fig.~\ref{fig:minimax_ARE} as a function of the support size $T$. Also illustrated in these figures is $\kappa_{\unif}$ which is the precision parameter corresponding to threshold values uniformly distribution over $\Theta = [-T,T]$, namely
\begin{align}
& \kappa_{\unif} \triangleq \min_{\theta \in [-T,T]} \frac{1}{2T}\int_{-T}^T \eta\left(t-\theta\right) dt \nonumber
 \\
& = 
\frac{1}{2T}\int_{-T}^{T} \eta\left(t\pm T\right) dt
= \frac{1}{2T}\int_{0}^{2T} \eta(t) dt  \label{eq:uniform_risk}. 
\end{align}
From Corollary~\ref{cor:LAN_thresh}, we conclude that the ARE under a uniform distribution is $\kappa_\unif \sigma^2$. \par

@@

\caption{\label{fig:minimax_support}
Optimal threshold density $\lambda^\star(dt)$ (blue) that maximizes the ARE for $f(x) = \Ncal(\theta,\sigma^2)$ and $\theta \in \Theta = [-T,T]$.
%
The continuous curve (red) represents the reciprocal of the asymptotic risk for at a fixed $\theta \in \Theta$ under the optimal density, so the minimax risk is the inverse of its minimal value. The dashed curve (green) is the reciprocal of the asymptotic risk for a fixed $\theta$ under a uniform distribution of threshold values over $\Theta$, hence its minimal value is the inverse of \eqref{eq:uniform_risk}. }
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\begin{tikzpicture}[scale = 0.55]
\begin{axis}[
width=8cm, height=6cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 1,
samples=10, 
xlabel= {$dt$},
xtick={-0.5,0,0.5},
xticklabels={-$T$, 0, $T$},
title = {$\sigma/\sigma_{\theta} = 1$},
ytick={0,1},
%ylabel = {$\lambda(dt)$},
yticklabels={0,1},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig1.csv};
%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
\end{axis}
\end{tikzpicture}
%
\begin{tikzpicture}[scale = 0.55]
\begin{axis}[
width=8cm, height=6cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 1,
samples=10, 
xlabel= {$dt$},
title = {$\sigma/\sigma_{\theta} = 2$},
xtick={-0.5,0,0.5},
xticklabels={-$T$, 0, $T$},
ytick={0,1},
ylabel = {$\lambda(dt)$},
yticklabels={0,1},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig2.csv};
%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
\end{axis}
\end{tikzpicture}
%
\begin{tikzpicture}[scale = 0.55]
\begin{axis}[
width=8cm, height=6cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 1,
samples=10, 
xlabel= {$dt$},
xtick={-0.5,0,0.5},
title = {$\sigma/\sigma_{\theta} = 3$},
xticklabels={-$T$, 0, $T$},
ytick={0,1},
%ylabel = {$\lambda(dt)$},
yticklabels={0,1},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig3.csv};
%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
\end{axis}
\end{tikzpicture}
%
\begin{tikzpicture}[scale = 0.55]
\begin{axis}[
width=8cm, height=6cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 1,
samples=10, 
xlabel= {$dt$},
title = {$\sigma/\sigma_{\theta} = 4$},
xtick={-0.5,0,0.5},
xticklabels={-$T$, 0, $T$},
ytick={0,1},
ylabel = {$\lambda(dt)$},
yticklabels={0,1},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig4.csv};
%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
\end{axis}
\end{tikzpicture}

\caption{\label{fig:opt_density}
Optimal threshold density $\lambda^\star(dt)$ that minimizes the asymptotic Bayes risk \eqref{eq:cvx_average} for a uniform prior with $\sigma/\sigma_\theta=1,2,3,4$, where $\sigma_\theta^2=T^2/3$ is the variance of the prior. 
}
\end{center}
\end{figure}

>>>>

\begin{thm} \label{thm:LAN1}
For $n \in \mathbb N$ and $A_n \subset \mathbb R$,  define
\begin{equation}
\label{eq:precision_general}
L_n(A_1,\ldots,A_n;\theta) \triangleq \frac{1}{n} \sum_{i=1}^n \frac{ \left(\frac{d}{d \theta} \Prob(X_i \in A_i) \right)^2 }{ \Prob(X_i \in A_i)\left(1- \Prob(X_i \in A_i) \right) }. 
\end{equation}
Consider the following conditions:
\begin{itemize}
\item [(i)\,\,] The probability density function $f(x)$ of $X_n-\theta$ is log-concave, differentiable, and symmetric. Furthermore, there exists $\delta>0$ such that the function $\eta^{1+\delta}(x)/f^\delta(x)$ is non-increasing in $|x|$. 
\item[(ii)\,] $A_n$ is a finite union of disjoint intervals.
\item[(iii)] The limit 
\begin{equation}
\label{eq:LAN_lim}
\kappa(\theta) \triangleq \lim_{n\to \infty} L_n(A_1,\ldots,A_n; \theta)
\end{equation}
exists. 
\end{itemize}
For $i=1,\ldots,n$ set
\[
B_n = \begin{cases} 1 & X_n \in A_n, \\
-1 & X_n \notin A_n. 
\end{cases} 
\]
For any $\theta$, $f(x)$ and a sequence of sets $A_1,A_2,\ldots$ such that (i)-(iii) hold, and any $h\in \mathbb R$, we have
\begin{align*}
& \log  \frac{ \mathbb P_{\theta+h/\sqrt{n}} (B_1,\ldots,B_n) }{
\mathbb P_{\theta} (B_1,\ldots,B_n)} \\
& \overset{d}{\longrightarrow} \Ncal\left(-\frac{1}{2} h^2 \kappa(\theta), h^2 \kappa(\theta) \right).
\end{align*} 
\end{thm}
Theorem~\ref{thm:LAN1} provides conditions under which $B_1,\ldots,B_n$ defines a LAN family with a precision parameter given by the limit in \eqref{eq:LAN_lim}. Condition (i) is satisfied, for example, by the normal distribution with $\delta\leq 2$. Condition (iii) is arguably the strongest and hardest to verify. As we show in Section~\ref{subsec:threshold} below, this condition is satisfied, for example, when $A_1, \ldots,A_n$ are half lines whose starting points are drawn independently from some probability measure on $\mathbb R$. Similar ideas imply that condition (iii) holds whenever we choose the intervals consisting each $A_i$ according to some pre-specified distribution. \par
%
An important conclusion of Theorem~\ref{thm:LAN1} follows from the local asymptotic minimax property of estimators in LAN models \cite{van2000asymptotic}):
\begin{cor} \label{cor:LA_minimax}
Let ${\theta}_n$ be an estimator of $\theta \in \Theta$ from $B_1,\ldots,B_n$ with detection regions $A_1,\ldots,A_n$ such that conditions (i)-(iii) of Theorem~\ref{thm:LAN1} hold. Then for any symmetric and quasi-convex function $L$, 
\begin{align*}
& \liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  \mathbb E \left[ L\left( \sqrt{n}({\theta}_{n} - \tau) \right) \right]
\\
& \qquad \qquad \qquad \qquad \geq \mathbb E \left[ L (Z/\sqrt{\kappa(\theta)}) \right],
\end{align*}
where $Z \sim \Ncal(0,1)$. In particular, for $L(x) = x^2$,
\begin{align*}
\liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  n \mathbb E  \left( {\theta}_{n} - \tau \right)^2 \geq 1/\kappa(\theta).
\end{align*}
\end{cor}
%
Corollary~\ref{cor:LA_minimax} says that when the sequence of one-bit messages defines a LAN model with respect to $\theta$, no estimator can attain MSE smaller than $1/\kappa(\theta)n + O(1/n)$ where $\kappa(\theta)$ is the precision parameter of the model. Consequently, the ARE  in such case is at most $\kappa(\theta)\sigma^2$. Furthermore, as we show next, no estimator in this setting can attain the optimal ARE of $\eta(0)\sigma^2$ uniformly over $ \Theta$.

@@

\subsection{Minimax Threshold Density}
The distribution $\lambda(dt)$ that maximizes $\kappa(\theta)$, and thus minimizes $1/\kappa(\theta)$, over the worst choice of $\theta$ in $\Theta$ is given as the solution to the following optimization problem:
\begin{align}
\label{eq:var_cvx_minimax}
\begin{split}
\mathrm{maximize} \quad &  \inf_{\theta \in \Theta} \int \eta(t-\theta) \lambda(dt)
\\ 
\mathrm{subject~to} 
\quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) \leq 1. 
\end{split}
\end{align}
The objective function in \eqref{eq:var_cvx_minimax} is concave in $\lambda(dt)$ and hence this problem can be solved using a convex program. We denote by $\kappa^\star$ the maximal value of \eqref{eq:var_cvx_minimax} and by $\lambda^\star(dt)$ the density that achieves this maximum. Theorem~\ref{thm:LAN1} and Corollary~\ref{cor:LAN_thresh} imply that for any $\theta \in \Theta$, the ARE of any local asymptotic minimax estimator (such as the ML estimator) from $\{B_i,\,i\in N\}$ of the form \eqref{eq:threshold_message} with $t_i \sim \lambda^\star$ i.i.d. is at least $\kappa^\star$.
%
%By discretizing the interval $[-b,b]$ using $N_\theta$ values $\theta_1,\ldots,\theta_{N_\theta}$ and the real line using $N_\lambda$ values $\lambda_1,\ldots,\lambda_{N_\lambda}$, the discrete version of \eqref{eq:var_cvx_minimax} is the following linear program (LP) in the variables $K \in \mathbb R$ and $\lambda \in \mathbb R^{N_\lambda}$:
%\begin{align}
%\label{eq:cvx_minimax}
%\begin{split}
%\mathrm{maximize} \quad &  K \\ 
%\mathrm{subject~to} 
%\quad &  K \leq \mathbf H\lambda \\
%& \lambda \geq 0,\quad   \mathbf 1^T\lambda  \leq 1,
%\end{split}
%\end{align}
%where $\mathbf H_{i,j} = \eta(t_i - \theta_j)$, $i=1,\ldots,N_\lambda$, $j = 1,\ldots,N_\theta$. 
%\begin{rem}
%The number of variables in \eqref{eq:cvx_minimax} is $N_\lambda+1$ and number of constraints is $1 + N_\lambda + N_\theta$. Since an LP has an optimal solution at which the number of constraints for which equality holds is no smaller than the number of variables \cite{papadimitriou1998combinatorial}, there exists an optimal $\lambda$ with support over no more than $N_{\theta}$ points. Therefore, in approximating the solution of \eqref{eq:var_cvx_minimax} using 
%\eqref{eq:cvx_minimax}, it is enough to take $N_\lambda = N_\theta$.
%\end{rem} 
\par
Figure~\ref{fig:minimax_support} illustrates an approximating to $\lambda^\star(dt)$ obtained by solving a discretized version of \eqref{eq:var_cvx_minimax} for the case when $f(x)$ is the normal density with variance $\sigma^2$ and $\Theta = [-T,T]$. The minimax asymptotic precision parameter $\kappa^\star$ obtained this way is illustrated in Fig.~\ref{fig:minimax_ARE} as a function of half the support size $T$. Also illustrated in these figures is $\kappa_{\unif}$ which is the precision parameter corresponding to threshold values uniformly distribution over $\Theta = [-T,T]$, namely
\begin{align}
& \kappa_{\unif} \triangleq \min_{\theta \in [-T,T]} \frac{1}{2T}\int_{-T}^T \eta\left(t-\theta\right) dt \nonumber
 \\
& = 
\frac{1}{2T}\int_{-T}^{T} \eta\left(t\pm T\right) dt
= \frac{1}{2T}\int_{0}^{2T} \eta(t) dt  \label{eq:uniform_risk}. 
\end{align}
Corollary~\ref{cor:LAN_thresh} implies that the ARE under threshold values uniformly distributed is $\kappa_\unif \sigma^2$. \par

@@

\caption{\label{fig:minimax_support}
Optimal threshold density $\lambda^\star(dt)$ (blue) that maximizes the ARE for $f(x) = \Ncal(\theta,\sigma^2)$ and $\theta \in [-T,T]$.
%
The continuous curve (red) represents the reciprocal of the asymptotic risk at a fixed $\theta \in [-T,T]$ under the optimal density, i.e., the minimax risk is the inverse of the minimal value of this curve. The dashed curve (green) is the reciprocal of the asymptotic risk at a fixed $\theta \in [-T,T]$ when the threshold values are uniformly distributed over $[-T,T]$, hence its minimal value is the inverse of \eqref{eq:uniform_risk}. }
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
%
\begin{tikzpicture}[scale = 0.55]
\begin{axis}[
width=8cm, height=6cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 1,
samples=10, 
xlabel= {$dt$},
title = {$\sigma/\sigma_{\theta} = 4$},
xtick={-0.5,0,0.5},
xticklabels={-$T$, 0, $T$},
ytick={0,1},
ylabel = {$\lambda(dt)$},
yticklabels={0,1},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig4.csv};
%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
\end{axis}
\end{tikzpicture}
%
\begin{tikzpicture}[scale = 0.55]
\begin{axis}[
width=8cm, height=6cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 1,
samples=10, 
xlabel= {$dt$},
xtick={-0.5,0,0.5},
title = {$\sigma/\sigma_{\theta} = 3$},
xticklabels={-$T$, 0, $T$},
ytick={0,1},
%ylabel = {$\lambda(dt)$},
yticklabels={0,1},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig3.csv};
%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
\end{axis}
\end{tikzpicture}
%
\begin{tikzpicture}[scale = 0.55]
\begin{axis}[
width=8cm, height=6cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 1,
samples=10, 
xlabel= {$dt$},
title = {$\sigma/\sigma_{\theta} = 2$},
xtick={-0.5,0,0.5},
xticklabels={-$T$, 0, $T$},
ytick={0,1},
ylabel = {$\lambda(dt)$},
yticklabels={0,1},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig2.csv};
%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
\end{axis}
\end{tikzpicture}
%
\begin{tikzpicture}[scale = 0.55]
\begin{axis}[
width=8cm, height=6cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 1,
samples=10, 
xlabel= {$dt$},
xtick={-0.5,0,0.5},
xticklabels={-$T$, 0, $T$},
title = {$\sigma/\sigma_{\theta} = 1$},
ytick={0,1},
%ylabel = {$\lambda(dt)$},
yticklabels={0,1},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig1.csv};
%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
\end{axis}
\end{tikzpicture}
\caption{\label{fig:opt_density}
Optimal threshold density $\lambda^\star(dt)$ that minimizes the asymptotic Bayes risk \eqref{eq:cvx_average} for a uniform prior with $\sigma/\sigma_\theta=1,2,3,4$, where $\sigma_\theta^2=T^2/3$ is the variance of the prior. 
}
\end{center}
\end{figure}
